The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/intro.tex
cite terzopolous

NURBS (Non-uniform Rational B Splines) are a popular higher-order modelling primitive which 
are used for computer-aided design (CAD), computational fabrication and computer animation. 
NURBS primitives were the first geometric representation used for physics-based animation, yet,
despite over three decades of research, animation of curved models such as those built with NURBS, remains a challenge.

>>>>

NURBS (Non-uniform Rational B Splines) are a popular higher-order modelling primitive which 
are used for computer-aided design (CAD), computational fabrication and computer animation. 
NURBS primitives were the first geometric representation used for physics-based animation~\cite{10.1145/37402.37427}, yet,
despite over three decades of research, animation of curved models such as those built with NURBS, remains a challenge.
